---
title: "Project 3"
output: html_document
---

My custom clustering function (cluster) runs many iterations of a random clustering algorithm
and chooses the best assignment based on separation, in this case average distance between cluster
centers, and compactness, in this case average within sum of squares for each cluster.

The user can specify whether or not they would like PCA to be done to the data before clustering using
the pca option. They can also specify the number of iterations ran. The last thing the user can specify
is the options a and b which are the weights for separation and compactness in the measurement for
determining the best cluster. Clusters are measured by the formula (a * separation) / (b * 
compactness), so a larger value of a places more weight on separation while a smaller value of b places
more weight on compactness. A larger value from this formula represents a better clustering.

```{r include=FALSE}
library(customClustering)
library(tidyverse)
```

```{r}
cluster(iris %>% select(-Species), 3)
```
```{r}
cluster(mtcars, 4, pca = TRUE, iterations = 1000)
```
